---
title: "countries_interest_rates"
author: "Nandhini Sridhar"
output: html_document
date: "2023-11-16"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


```{r}
library(tidyverse)
library(readxl)
library(ggplot2)
library(fuzzyjoin) #fuzzy matching of strings
library(lfe) #fixed effects regression
library(fixest) #fixed effects regression
library(expss) #tables

#packages
#lfe - install.packages("lfe")
#fixest - install.packages("fixest")
#expss - install.packages("expss)
```

DATA CLEANING
```{r}
setwd("/Users/NandhiniSridhar/Desktop/econ_honors_thesis")
mfdata <- read_excel("/Users/NandhiniSridhar/Desktop/econ_honors_thesis/data/Microfinance/mix-market-financial-performance-dataset-in-usd.xlsx")
#View(mfdata)

country_data <- read_excel("/Users/NandhiniSridhar/Desktop/econ_honors_thesis/data/Microfinance/COUNTRY_CODEBOOKmix-market-mfi-company-metadata.xlsx")
#View(country_data)

names(mfdata) <- gsub(' ', '_', names(mfdata))
names(country_data) <- gsub(' ', '_', names(country_data))

ir <- read_excel("/Users/NandhiniSridhar/Desktop/econ_honors_thesis/data/Microfinance/Interest_Rates.xlsx")
colnames(ir)
cols <- c("Country", "Scale", "Base Year")
for (i in 2000:2021){
  cols <- cols %>% append(i)
}
print(cols)
names(ir) <- cols
ir <- ir[6:nrow(ir),]
```

```{r}
mfdata['Country'] <- NA
countries <- c()
enter <- c()
ifc <- c()
elsec <- c()
names <- c()

#get the countries of each bank in the mfi dataset
for (i in 1:nrow(mfdata)) {
  mfi_name <- mfdata$MFI_Name[i]
  enter <- enter %>% append(1)
  
  if(mfi_name %in% country_data$MFI_Name){
    ifc <- ifc %>% append(1)
    country_name <- country_data$Country[country_data$MFI_Name == mfi_name]
    names <- names %>% append(length(country_name))
    countries <- countries %>% append(country_name)
    #mfdata[i, 'country'] <- country_name
  }
  else{
    elsec <- elsec %>% append(1)
    countries <- countries %>% append("NOT FOUND")
  }
}

# get rid of ones with multiple countries (would have repeats of the same country for some reason)
names2 <- c()
for(i in 1:length(names)){
  if(names[i] == 2){
    names2 <- names2 %>% append(1)
    cat(names[i], ": ", countries[i], "\n")
    countries <- countries[-i]
  }
}

#append to mfi dataset
mfdata$Country <- countries
```

```{r}
#arrange by MFI name and fiscal year
mfdata <- mfdata %>% filter(Period_Type == "ANN") %>% arrange(MFI_Name, Fiscal_Year)
#mfdata['country_reduced'] <- gsub(",.*", "", mfdata$country)
#mfdata['country_reduced'] <- gsub("\\(.*", "", mfdata$country)
#names(country_data) <- gsub(' ', '_', names(country_data))

mf_interest <- stringdist_join(mfdata, ir, 
                by='Country', 
                mode='left',
                method = "soundex") %>%
  arrange(Country.x)


#Ratio_GLP_Female is the y variable - the percentage of loan money that goes to women borrowers
mf_interest %>% drop_na(`Gross_Loan_Portfolio`)
mf_interest %>% drop_na(`Gross_Loan_Portfolio_>_Gender_>_Female`)

mf_interest$Ratio_GLP_Female = mf_interest$`Gross_Loan_Portfolio_>_Gender_>_Female` / mf_interest$Gross_Loan_Portfolio
mfdata$Ratio_GLP_Female = mfdata$`Gross_Loan_Portfolio_>_Gender_>_Female` / mfdata$Gross_Loan_Portfolio
```

```{r}
#encode by region
#World Bank region classifications: Africa, East Asia & the Pacific, Europe & Central Asia, Latin America & The Caribbean, Middle East & North Africa, South Asia
africa <- c("Angola", "Benin", "Botswana", "Burkina Faso", "Burundi", "Cameroon", "Cabo Verde", "Central African Republic", "Chad", "Comoros", "Cote d'Ivore", "Cote d'Ivoire (Ivory Coast)", "Congo", "Congo, Democratic Republic of the","Congo, Republic of the", "Equitorial Guinea", "Eritrea", "Eswatini", "Ethiopia", "Gabon", "Ghana", "Gambia", "Gambia, The", "Guinea", "Guinea-Bissau", "Kenya", "Lesotho", "Liberia", "Madagascar", "Malawi", "Mali", "Mauritus", "Mozambique", "Nambia", "Niger", "Nigeria", "Rwanda", "Senegal", "Sierra Leone", "Somalia", "South Africa", "South Sudan", "Sudan", "Tanzania", "Togo", "Uganda", "Zambia", "Zimbabwe", "Namibia", "Swaziland")

east_asia_pacific <- c("Cambodia", "China", "China, People's Republic of", "Indonesia", "Korea", "Lao PDR", "Malaysia", "Mongolia", "Myanmar", "Papua New Guinea", "Philippines", "Singapore", "Thailand", "Vietnam", "East Timor", "Laos", "Myanmar (Burma)", "Samoa", "Solomon Islands", "Tonga", "Vanuatu")

europe_central_asia <- c("Albania", "Armenia", "Azerbaijan", "Belarus", "Bosnia and Herzegovina", "Bulgaria", "Croatia", "Georgia", "Hungary", "Kazakhstan", "Kosovo", "Kyrgyzstan", "Moldova", "Montenegro", "Macedonia", "Poland", "Romania", "Russia", "Serbia", "Tajikistan", "Turkey", "Turkmenistan", "Ukraine", "Uzbekistan", "Slovakia")

latin_america_caribbean <- c("Argentina", "Belize", "Bolivia", "Brazil", "Colombia", "Chile", "Costa Rica", "Dominican Republic", "Ecuador", "El Salvador", "Grenada", "Guatemala", "Guyana", "Haiti", "Honduras", "Jamaica", "Mexico", "Nicaragua", "Panama", "Paraguay", "Peru", "Saint Lucia", "Suriname", "Trinidad and Tobago", "Uruguay", "Venezuela", "Fiji")

middle_east_north_africa <- c("Algeria", "Bahrain", "Djibouti", "Egypt", "Iran", "Iraq", "Jordan", "Kuwait", "Lebanon", "Libya", "Morocco", "Oman", "Palestine", "Qatar", "Saudi Arabia", "Syria", "Tunisia", "United Arab Emirates", "Yemen", "Israel")

south_asia <- c("Sri Lanka", "Bangladesh", "India", "Afghanistan", "Pakistan", "Bhutan", "Nepal", "Maldives")

north_america <- c("United States", "Canada")

mfdata <- mfdata %>% 
  mutate(Region = case_when(
    Country %in% africa ~ 'Sub_Saharan_Africa',
    Country %in% east_asia_pacific ~ 'East_Asia_Pacific',
    Country %in% europe_central_asia ~ 'Europe_Central_Asia',
    Country %in% middle_east_north_africa ~ 'Middle_East_North_Africa',
    Country %in% north_america ~ 'North_America',
    Country %in% latin_america_caribbean ~ 'Latin_America_Caribbean',
    Country %in% south_asia ~ 'South_Asia',
    TRUE ~ 'Other'))

mf_interest <- mf_interest %>% 
  mutate(Region = case_when(
    Country.x %in% africa ~ 'Sub_Saharan_Africa',
    Country.x %in% east_asia_pacific ~ 'East_Asia_Pacific',
    Country.x %in% europe_central_asia ~ 'Europe_Central_Asia',
    Country.x %in% middle_east_north_africa ~ 'Middle_East_North_Africa',
    Country.x %in% north_america ~ 'North_America',
    Country.x %in% latin_america_caribbean ~ 'Latin_America_Caribbean',
    Country.x %in% south_asia ~ 'South_Asia',
    TRUE ~ 'Other'))

x <- mf_interest %>% filter(Region == "Other") %>% select(Country.x)
print(unique(x))
```

```{r}
# instrumental variable is the interest rate for a given year
# here i create the variable that can be used as a common instrument (interest rates are originally split one year per column)
# here i only take the interest rate that directly corresponds to the fiscal year for a given entry

mf_interest$Cur_Interest_Rate = 9999 #this is the error code


for(i in 1:nrow(mf_interest)){
  year = mf_interest$Fiscal_Year[i]
  if(mf_interest$Fiscal_Year[i] != 1999){
    if(mf_interest[i, as.character(year)] != "..." & !is.na(mf_interest[i, as.character(year)]) & mf_interest[i, as.character(year)] != "-"){
      #print(i)
      #print(mf_interest[i, as.character(year)])
      mf_interest$Cur_Interest_Rate[i] <- mf_interest[i, as.character(year)]
    }
  }
  #if(suppressWarnings(is.na(as.numeric(mf_interest$Cur_Interest_Rate))[i])){
  #  print(mf_interest$Cur_Interest_Rate[i])
  #}
}
#unique(mf_interest$Cur_Interest_Rate)

mf_interest$Cur_Interest_Rate <- as.numeric(mf_interest$Cur_Interest_Rate)
```

```{r}
mf_interest <- mf_interest %>% drop_na("Gross_Loan_Portfolio")
mf_interest <- mf_interest %>% drop_na("Ratio_GLP_Female")
mf_interest <- mf_interest %>% drop_na("Percent_of_female_borrowers")


working_mf_interest <- mf_interest %>% filter(Cur_Interest_Rate != 9999)
working_mf_interest <- working_mf_interest %>% drop_na("Cur_Interest_Rate")
```

```{r}
#run everything above this to clean and preprocess data
```

TABLES, GRAPHS, AND FIGURES

Tables
```{r}
#use for GLP, %women borrowers, %GLP to women over time for all data
mfdata_no_null <- mfdata %>% drop_na(Gross_Loan_Portfolio)
mfdata_no_null <- mfdata_no_null %>% drop_na(Percent_of_female_borrowers)
mfdata_no_null <- mfdata_no_null %>% drop_na(`Number_of_active_borrowers_>_Gender_>_Female`)
mfdata_no_null <- mfdata_no_null %>% drop_na(Ratio_GLP_Female)

year_totals_all <- data.frame(matrix(ncol=5, nrow=0))
colnames(year_totals_all) <- c("Fiscal Year", "Average Gross Loan Portfolio", "Average Percent Female Borrowers", "Average Fraction GLP To Women", "Average Number Female Borrowers")
min_year_all <- min(mfdata_no_null$Fiscal_Year)
max_year_all <- max(mfdata_no_null$Fiscal_Year)

year_totals <- data.frame(matrix(ncol=5, nrow=0))
colnames(year_totals) <- c("Fiscal Year", "Average Gross Loan Portfolio", "Average Percent Female Borrowers", "Average Fraction GLP To Women", "Average Number Female Borrowers")
min_year <- min(working_mf_interest$Fiscal_Year)
max_year <- max(working_mf_interest$Fiscal_Year)


#stats by year for all data
row <- 1
for(i in min_year_all:max_year_all){
  year_totals_all[row, "Fiscal Year"] <- i
  temp <- mfdata %>% filter(Fiscal_Year == i)
  temp <- temp %>% drop_na(Gross_Loan_Portfolio)
  temp <- temp %>% drop_na(Percent_of_female_borrowers)
  temp <- temp %>% drop_na(`Number_of_active_borrowers_>_Gender_>_Female`)
  temp <- temp %>% drop_na(Ratio_GLP_Female)


  #print(drop_na(temp$Gross_Loan_Portfolio) %>% mean())
  year_totals_all[row, "Average Gross Loan Portfolio"] <- mean(temp$Gross_Loan_Portfolio)
  year_totals_all[row, "Average Percent Female Borrowers"] <- mean(temp$Percent_of_female_borrowers)
  year_totals_all[row, "Average Fraction GLP To Women"] <- mean(temp$`Number_of_active_borrowers_>_Gender_>_Female`)
  year_totals_all[row, "Average Number Female Borrowers"] <- mean(temp$Ratio_GLP_Female)
  row = row + 1
}

#stats by year for working data
row <- 1
for(i in min_year:max_year){
  year_totals[row, "Fiscal Year"] <- i
  temp <- working_mf_interest %>% filter(Fiscal_Year == i)
  year_totals[row, "Average Gross Loan Portfolio"] <- mean(temp$Gross_Loan_Portfolio)
  year_totals[row, "Average Percent Female Borrowers"] <- mean(temp$Percent_of_female_borrowers)
  year_totals[row, "Average Fraction GLP To Women"] <- mean(temp$`Number_of_active_borrowers_>_Gender_>_Female`)
  year_totals[row, "Average Number Female Borrowers"] <- mean(temp$Ratio_GLP_Female)
  row = row + 1
}


print(year_totals_all %>% setDT())
print(year_totals %>% setDT())
```
```{r}
#number of observations in each table I use
num_obs <- data.frame("Dataframe" = c("Full Dataset", "Full Dataset Without Nulls", "Working Dataset"), Rows=c(nrow(mfdata), nrow(mfdata_no_null), nrow(working_mf_interest)))
num_obs$"Number of Countries" <- c(length(unique(mfdata$Country)), length(unique(mfdata_no_null$Country)), length(unique(working_mf_interest$Country.x)))
num_obs$"Number of MFIs" <- c(length(unique(mfdata$MFI_ID)), length(unique(mfdata_no_null$MFI_ID)), length(unique(working_mf_interest$MFI_ID)))

num_obs_table <- setDT(num_obs)
print(num_obs_table)
```


```{r}
#stats for entire dataset
mfdata_no_null <- mfdata_no_null %>% apply_labels(
  Gross_Loan_Portfolio = "Gross Loan Portfolio",
  Percent_of_female_borrowers = "Percent of Female Borrowers",
  Ratio_GLP_Female = "Fraction of GLP to Female Borrowers",
  `Number_of_active_borrowers_>_Gender_>_Female` = "Number of Female Borrowers",
  Region = "Percent of Data From Regions"
)

mf_table <- mfdata_no_null %>% 
  tab_total_label("All MIX Market Data") %>%
  tab_cells(Gross_Loan_Portfolio) %>%
  tab_stat_mean() %>%
  tab_cells(Percent_of_female_borrowers) %>%
  tab_stat_mean() %>%
  tab_cells(Ratio_GLP_Female) %>%
  tab_stat_mean() %>%
  #percent of data from each region
  tab_cells(Region) %>%
  tab_stat_cpct() %>%
  tab_pivot()

#mf_table


```


```{r}

working_mf_interest <- working_mf_interest %>% apply_labels(
  Gross_Loan_Portfolio = "Gross Loan Portfolio",
  Percent_of_female_borrowers = "Percent of Female Borrowers",
  Ratio_GLP_Female = "Fraction of GLP to Female Borrowers",
  `Number_of_active_borrowers_>_Gender_>_Female` = "Number of Female Borrowers",
  Region = "Percent of Data From Regions"
)

working_mf_table <- working_mf_interest %>% 
  tab_total_label("Working MIX Market Data") %>%
  tab_cells(Gross_Loan_Portfolio) %>%
  tab_stat_mean() %>%
  tab_cells(Percent_of_female_borrowers) %>%
  tab_stat_mean() %>%
  tab_cells(Ratio_GLP_Female) %>%
  tab_stat_mean() %>%
  #percent of data from each region
  tab_cells(Region) %>%
  tab_stat_cpct() %>%
  tab_pivot()


#i think this achieves the two column effect with the same summary stats for the diff datasets
combined_table <- mf_table %>% merge(working_mf_table)
#working_mf_table
#mf_table
combined_table
```

Graphs
```{r}
#mfdata - all MIX Market data
print(length(unique(mfdata$MFI_Name)))
print(length(unique(mfdata$Country.x)))

ggplot(mfdata, aes(x=Country)) + 
  geom_bar() +
  theme(axis.text.x = element_text(size=5, angle = 90, vjust = 1, hjust=1)) + 
  labs(title="Number of MFIs Reporting Across All Years, By Country", x="Country", y="Number of MFIs")

ggplot(year_totals_all, aes(x=Fiscal_Year, y=Gross_Loan_Portfolio)) +
  geom_line() +
  scale_x_continuous(breaks = seq(min(year_totals_all$Fiscal_Year), max(year_totals_all$Fiscal_Year), by=1)) +
  scale_y_continuous(trans='log10') + 
  labs(title = "Gross Loan Portfolios Over Time Across all MFIs - All Data", x="Fiscal Year", y="Gross Loan Portfolio - Log Scaled")
  
```

```{r}
#working data - mfis with interest data for relevant years
print(length(unique(working_mf_interest$MFI_Name)))
print(length(unique(working_mf_interest$Country.x)))

ggplot(working_mf_interest, aes(x=Country.x)) + 
  geom_bar() +
  theme(axis.text.x = element_text(size=5, angle = 90, vjust = 1, hjust=1)) + 
  labs(title="MFIs") +
  labs(title="Number of MFIs Reporting Across All Years, By Country", x="Country", y="Number of MFIs")

ggplot(year_totals, aes(x=Fiscal_Year, y=Gross_Loan_Portfolio)) +
  geom_line() +
  scale_x_continuous(breaks = seq(min(year_totals$Fiscal_Year), max(year_totals$Fiscal_Year), by=1)) +
  labs(title = "Gross Loan Portfolios Over Time Across all MFIs - Working Data", x="Fiscal Year", y="Gross Loan Portfolio")
  
```

REGRESSIONS FROM HERE AND BELOW
```{r}
#basic model, no fixed effects
basic_linear <- lm(Ratio_GLP_Female ~ Gross_Loan_Portfolio, data=mf_interest)
summary(basic_linear)

basic_log <- lm(Ratio_GLP_Female ~ log(Gross_Loan_Portfolio), data=mf_interest)
summary(basic_log)


#With time and mfi fixed effects
#the 0 means no instrumental variables
#what standard error clustering dim do i use (right now doing it by mfi)
time_mfi_fe <- felm(Ratio_GLP_Female ~ log(Gross_Loan_Portfolio) | MFI_Name + Fiscal_Year | 0 | MFI_Name, mf_interest)
summary(time_mfi_fe)

#negative coef

#include region fixed effects
time_region_fe <- felm(Ratio_GLP_Female ~ log(Gross_Loan_Portfolio) | Region + Fiscal_Year | 0 | MFI_Name, mf_interest)
summary(time_region_fe)

```


```{r}
#instrumental variable only, no fixed effects, still using log of GLP

#looking at raw change in GLP based on change in interest rate (which is already in percentage points)
#dont use
ir_inst_step1 <- lm(Gross_Loan_Portfolio ~ Cur_Interest_Rate, data=working_mf_interest)
summary(ir_inst_step1)
working_mf_interest$predicted_GLP <- predict(ir_inst_step1)

ir_inst_step2 <- lm(Ratio_GLP_Female ~ log(predicted_GLP), data = working_mf_interest)
summary(ir_inst_step2)


#looking at percent change in GLP based on change in interest rate (which is already in percentage points)
ir_log_inst_step1 <- lm(log(Gross_Loan_Portfolio) ~ Cur_Interest_Rate, data=working_mf_interest)
summary(ir_log_inst_step1)
working_mf_interest$predicted_GLP <- predict(ir_log_inst_step1)

ir_log_inst_step2 <- lm(Ratio_GLP_Female ~ log(predicted_GLP), data = working_mf_interest)
summary(ir_log_inst_step2)
```
```{r}
summary(mf_interest$Percent_of_female_borrowers)
sd(mf_interest$Percent_of_female_borrowers)
summary(mf_interest$Gross_Loan_Portfolio)
sd(mf_interest$Gross_Loan_Portfolio)
sd(log(mf_interest$Gross_Loan_Portfolio))

```

```{r}
#percent is from 0 to 1

time_mfi_fe <- felm(Percent_of_female_borrowers ~ log(Gross_Loan_Portfolio) | MFI_Name + Fiscal_Year | 0 | MFI_Name, mf_interest)
summary(time_mfi_fe)

time_region_fe <- felm(Percent_of_female_borrowers ~ log(Gross_Loan_Portfolio) | Country.x + Fiscal_Year | 0 | MFI_Name, mf_interest)
summary(time_region_fe)

#include region fixed effects
time_region_fe <- felm(Percent_of_female_borrowers ~ log(Gross_Loan_Portfolio) | Region + Fiscal_Year | 0 | MFI_Name, mf_interest)
summary(time_region_fe)

```



These are the main regressions I use
Includes both time and cross sectional fixed effects and interest rate as an instrumental variable

Cross sectional fixed effect by MFI
```{r}
working_mf_interest <- working_mf_interest %>% filter(Region == "South_Asia" | Region == "Latin_America_Caribbean" | Region == "Sub_Saharan_Africa")

fe_inst_1 <- feols(log(Gross_Loan_Portfolio) ~ Cur_Interest_Rate | MFI_Name + Fiscal_Year, cluster="MFI_Name", data=working_mf_interest, )
summary(fe_inst_1)

working_mf_interest$predicted_log_GLP <- predict(fe_inst_1, new_data=working_mf_interest$predicted_log_GLP)

fe_inst_2 <- feols(Ratio_GLP_Female ~ predicted_log_GLP | MFI_Name + Fiscal_Year, cluster="MFI_Name", data=working_mf_interest)
summary(fe_inst_2)
```

Cross sectional fixed effect by region
```{r}
#first stage here is weak so second stage isn't working, fixed effects are doing everything
working_mf_interest <- working_mf_interest %>% filter(Region == "South_Asia" | Region == "Latin_America_Caribbean" | Region == "Sub_Saharan_Africa")

fe_inst_1 <- feols(log(Gross_Loan_Portfolio) ~ Cur_Interest_Rate | Region + Fiscal_Year, cluster="MFI_Name", data=working_mf_interest, )
summary(fe_inst_1)

working_mf_interest$predicted_log_GLP <- predict(fe_inst_1, new_data=working_mf_interest$predicted_log_GLP)

fe_inst_2 <- feols(Percent_of_female_borrowers ~ predicted_log_GLP | Region + Fiscal_Year, cluster="MFI_Name", data=working_mf_interest)
summary(fe_inst_2)
```
Cross sectional fixed effect by country
```{r}
working_mf_interest <- working_mf_interest %>% filter(Region == "South_Asia" | Region == "Latin_America_Caribbean" | Region == "Sub_Saharan_Africa")

fe_inst_1 <- feols(log(Gross_Loan_Portfolio) ~ Cur_Interest_Rate | Country.x + Fiscal_Year, cluster="MFI_Name", data=working_mf_interest, )
summary(fe_inst_1)

working_mf_interest$predicted_log_GLP <- predict(fe_inst_1, new_data=working_mf_interest$predicted_log_GLP)

fe_inst_2 <- feols(Ratio_GLP_Female ~ predicted_log_GLP | Country.x + Fiscal_Year, cluster="MFI_Name", data=working_mf_interest)
summary(fe_inst_2)
```

```{r}
# run above for all tables/graphs/analysis
```




Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
