---
title: "robustness_checks_pt2"
output: html_document
date: "2024-02-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(readxl)
library(ggplot2)
library(fuzzyjoin) #fuzzy matching of strings
library(lfe) #fixed effects regression
library(fixest) #fixed effects regression
library(expss) #tables
library(gtsummary) #output regression results to table


#packages
#lfe - install.packages("lfe")
#fixest - install.packages("fixest")
#expss - install.packages("expss)
#gtsummary - install.packages("gtsummary")

```

DATA CLEANING
```{r}
setwd("/Users/NandhiniSridhar/Desktop/econ_honors_thesis")
mfdata <- read_excel("/Users/NandhiniSridhar/Desktop/econ_honors_thesis/data/Microfinance/mix-market-financial-performance-dataset-in-usd.xlsx")
#View(mfdata)

country_data <- read_excel("/Users/NandhiniSridhar/Desktop/econ_honors_thesis/data/Microfinance/COUNTRY_CODEBOOKmix-market-mfi-company-metadata.xlsx")
#View(country_data)

names(mfdata) <- gsub(' ', '_', names(mfdata))
names(country_data) <- gsub(' ', '_', names(country_data))

ir <- read_excel("/Users/NandhiniSridhar/Desktop/econ_honors_thesis/data/Microfinance/Interest_Rates.xlsx")
colnames(ir)
cols <- c("Country", "Scale", "Base Year")
for (i in 2000:2021){
  cols <- cols %>% append(i)
}
print(cols)
names(ir) <- cols
ir <- ir[6:nrow(ir),]
```

```{r}
mfdata['Country'] <- NA
countries <- c()
enter <- c()
ifc <- c()
elsec <- c()
names <- c()

#get the countries of each bank in the mfi dataset
for (i in 1:nrow(mfdata)) {
  mfi_name <- mfdata$MFI_Name[i]
  enter <- enter %>% append(1)
  
  if(mfi_name %in% country_data$MFI_Name){
    ifc <- ifc %>% append(1)
    country_name <- country_data$Country[country_data$MFI_Name == mfi_name]
    names <- names %>% append(length(country_name))
    countries <- countries %>% append(country_name)
    #mfdata[i, 'country'] <- country_name
  }
  else{
    elsec <- elsec %>% append(1)
    countries <- countries %>% append("NOT FOUND")
  }
}

# get rid of ones with multiple countries (would have repeats of the same country for some reason)
names2 <- c()
for(i in 1:length(names)){
  if(names[i] == 2){
    names2 <- names2 %>% append(1)
    cat(names[i], ": ", countries[i], "\n")
    countries <- countries[-i]
  }
}

#append to mfi dataset
mfdata$Country <- countries
```
```{r}
print(nrow(mfdata))
mfdata <- mfdata %>% drop_na("Gross_Loan_Portfolio")
mfdata <- mfdata %>% drop_na("Percent_of_female_borrowers")
mfdata <- mfdata %>% drop_na(`Gross_Loan_Portfolio_>_Gender_>_Female`)
print(nrow(mfdata))

mfdata$Ratio_GLP_Female = mfdata$`Gross_Loan_Portfolio_>_Gender_>_Female` / mfdata$Gross_Loan_Portfolio
print(nrow(mfdata))
mfdata <- mfdata %>% filter(Ratio_GLP_Female <= 1)
```

```{r}
#arrange by MFI name and fiscal year
mfdata <- mfdata %>% filter(Period_Type == "ANN") %>% arrange(MFI_Name, Fiscal_Year)
#mfdata['country_reduced'] <- gsub(",.*", "", mfdata$country)
#mfdata['country_reduced'] <- gsub("\\(.*", "", mfdata$country)
#names(country_data) <- gsub(' ', '_', names(country_data))

mf_interest <- stringdist_join(mfdata, ir, 
                by='Country', 
                mode='left',
                method = "soundex") %>%
  arrange(Country.x)


#Ratio_GLP_Female is the y variable - the percentage of loan money that goes to women borrowers
mf_interest %>% drop_na(`Gross_Loan_Portfolio`)
mf_interest %>% drop_na(`Gross_Loan_Portfolio_>_Gender_>_Female`)

mf_interest$Ratio_GLP_Female = mf_interest$`Gross_Loan_Portfolio_>_Gender_>_Female` / mf_interest$Gross_Loan_Portfolio
```

```{r}
#encode by region
#World Bank region classifications: Africa, East Asia & the Pacific, Europe & Central Asia, Latin America & The Caribbean, Middle East & North Africa, South Asia
africa <- c("Angola", "Benin", "Botswana", "Burkina Faso", "Burundi", "Cameroon", "Cabo Verde", "Central African Republic", "Chad", "Comoros", "Cote d'Ivore", "Cote d'Ivoire (Ivory Coast)", "Congo", "Congo, Democratic Republic of the","Congo, Republic of the", "Equitorial Guinea", "Eritrea", "Eswatini", "Ethiopia", "Gabon", "Ghana", "Gambia", "Gambia, The", "Guinea", "Guinea-Bissau", "Kenya", "Lesotho", "Liberia", "Madagascar", "Malawi", "Mali", "Mauritus", "Mozambique", "Nambia", "Niger", "Nigeria", "Rwanda", "Senegal", "Sierra Leone", "Somalia", "South Africa", "South Sudan", "Sudan", "Tanzania", "Togo", "Uganda", "Zambia", "Zimbabwe", "Namibia", "Swaziland")

east_asia_pacific <- c("Cambodia", "China", "China, People's Republic of", "Indonesia", "Korea", "Lao PDR", "Malaysia", "Mongolia", "Myanmar", "Papua New Guinea", "Philippines", "Singapore", "Thailand", "Vietnam", "East Timor", "Laos", "Myanmar (Burma)", "Samoa", "Solomon Islands", "Tonga", "Vanuatu")

europe_central_asia <- c("Albania", "Armenia", "Azerbaijan", "Belarus", "Bosnia and Herzegovina", "Bulgaria", "Croatia", "Georgia", "Hungary", "Kazakhstan", "Kosovo", "Kyrgyzstan", "Moldova", "Montenegro", "Macedonia", "Poland", "Romania", "Russia", "Serbia", "Tajikistan", "Turkey", "Turkmenistan", "Ukraine", "Uzbekistan", "Slovakia")

latin_america_caribbean <- c("Argentina", "Belize", "Bolivia", "Brazil", "Colombia", "Chile", "Costa Rica", "Dominican Republic", "Ecuador", "El Salvador", "Grenada", "Guatemala", "Guyana", "Haiti", "Honduras", "Jamaica", "Mexico", "Nicaragua", "Panama", "Paraguay", "Peru", "Saint Lucia", "Suriname", "Trinidad and Tobago", "Uruguay", "Venezuela", "Fiji")

middle_east_north_africa <- c("Algeria", "Bahrain", "Djibouti", "Egypt", "Iran", "Iraq", "Jordan", "Kuwait", "Lebanon", "Libya", "Morocco", "Oman", "Palestine", "Qatar", "Saudi Arabia", "Syria", "Tunisia", "United Arab Emirates", "Yemen", "Israel")

south_asia <- c("Sri Lanka", "Bangladesh", "India", "Afghanistan", "Pakistan", "Bhutan", "Nepal", "Maldives")

north_america <- c("United States", "Canada")

mfdata <- mfdata %>% 
  mutate(Region = case_when(
    Country %in% africa ~ 'Sub_Saharan_Africa',
    Country %in% east_asia_pacific ~ 'East_Asia_Pacific',
    Country %in% europe_central_asia ~ 'Europe_Central_Asia',
    Country %in% middle_east_north_africa ~ 'Middle_East_North_Africa',
    Country %in% north_america ~ 'North_America',
    Country %in% latin_america_caribbean ~ 'Latin_America_Caribbean',
    Country %in% south_asia ~ 'South_Asia',
    TRUE ~ 'Other'))

mf_interest <- mf_interest %>% 
  mutate(Region = case_when(
    Country.x %in% africa ~ 'Sub_Saharan_Africa',
    Country.x %in% east_asia_pacific ~ 'East_Asia_Pacific',
    Country.x %in% europe_central_asia ~ 'Europe_Central_Asia',
    Country.x %in% middle_east_north_africa ~ 'Middle_East_North_Africa',
    Country.x %in% north_america ~ 'North_America',
    Country.x %in% latin_america_caribbean ~ 'Latin_America_Caribbean',
    Country.x %in% south_asia ~ 'South_Asia',
    TRUE ~ 'Other'))

x <- mf_interest %>% filter(Region == "Other") %>% select(Country.x)
print(unique(x))
```

```{r}
# instrumental variable is the interest rate for a given year
# here i create the variable that can be used as a common instrument (interest rates are originally split one year per column)
# here i only take the interest rate that directly corresponds to the fiscal year for a given entry

mf_interest$Cur_Interest_Rate = 9999 #this is the error code


for(i in 1:nrow(mf_interest)){
  year = mf_interest$Fiscal_Year[i]
  if(mf_interest$Fiscal_Year[i] != 1999){
    if(mf_interest[i, as.character(year)] != "..." & !is.na(mf_interest[i, as.character(year)]) & mf_interest[i, as.character(year)] != "-"){
      #print(i)
      #print(mf_interest[i, as.character(year)])
      mf_interest$Cur_Interest_Rate[i] <- mf_interest[i, as.character(year)]
    }
  }
  #if(suppressWarnings(is.na(as.numeric(mf_interest$Cur_Interest_Rate))[i])){
  #  print(mf_interest$Cur_Interest_Rate[i])
  #}
}
#unique(mf_interest$Cur_Interest_Rate)

mf_interest$Cur_Interest_Rate <- as.numeric(mf_interest$Cur_Interest_Rate)
```

```{r}
mf_interest <- mf_interest %>% drop_na("Gross_Loan_Portfolio")
mf_interest <- mf_interest %>% drop_na("Ratio_GLP_Female")
mf_interest <- mf_interest %>% drop_na("Percent_of_female_borrowers")


working_mf_interest <- mf_interest %>% filter(Cur_Interest_Rate != 9999)
working_mf_interest <- working_mf_interest %>% drop_na("Cur_Interest_Rate")
working_mf_interest <- working_mf_interest %>% filter(Region == "South_Asia" | Region == "Latin_America_Caribbean" | Region == "Sub_Saharan_Africa")
```

```{r}
#run everything above this to clean and preprocess data
```

# Run with only data 2006-2017

```{r}
working_no_2019 <- working_mf_interest %>% filter(Fiscal_Year < 2018 & Fiscal_Year > 2006)
```

## Now we run the same regressions and make the same tables


```{r}
working_no_2019 <- working_no_2019 %>% apply_labels(
  Gross_Loan_Portfolio = "Gross Loan Portfolio",
  Percent_of_female_borrowers = "Percent of Female Borrowers",
  Ratio_GLP_Female = "Fraction of GLP to Female Borrowers",
  `Number_of_active_borrowers_>_Gender_>_Female` = "Number of Female Borrowers",
  Region = "Percent of Data From Regions",
  Cur_Interest_Rate = "Current Interest Rate"
)


```

## Percent of Female Borrowers

```{r}
basic_linear <- lm(Percent_of_female_borrowers ~ Gross_Loan_Portfolio, data=working_no_2019)
print(summary(basic_linear))

basic_log <- lm(Percent_of_female_borrowers ~ log(Gross_Loan_Portfolio), data=working_no_2019)
print(summary(basic_log))
```


```{r}
#Fixed effects, no instrument
time_mfi_fe_pct <- felm(Percent_of_female_borrowers ~ log(Gross_Loan_Portfolio) | MFI_Name + Fiscal_Year | 0 | MFI_Name, working_no_2019)
print(summary(time_mfi_fe_pct))

time_country_fe_pct <- felm(Percent_of_female_borrowers ~ log(Gross_Loan_Portfolio) | Country.x + Fiscal_Year | 0 | MFI_Name, working_no_2019)
print(summary(time_country_fe_pct))

#include region fixed effects
time_region_fe_pct <- felm(Percent_of_female_borrowers ~ log(Gross_Loan_Portfolio) | Region + Fiscal_Year | 0 | MFI_Name, working_no_2019)
print(summary(time_region_fe_pct))
```
```{r}
fe_inst_1_mfi <- feols(log(Gross_Loan_Portfolio) ~ Cur_Interest_Rate | MFI_Name + Fiscal_Year, cluster="MFI_Name", data=working_no_2019, )
print(summary(fe_inst_1_mfi))

working_no_2019$predicted_log_GLP <- predict(fe_inst_1_mfi, new_data=working_no_2019$predicted_log_GLP)

fe_inst_2_mfi <- feols(Percent_of_female_borrowers ~ predicted_log_GLP | MFI_Name + Fiscal_Year, cluster="MFI_Name", data=working_no_2019)
print(summary(fe_inst_2_mfi))
```
```{r}
fe_inst_1_country <- feols(log(Gross_Loan_Portfolio) ~ Cur_Interest_Rate | Region + Fiscal_Year, cluster="MFI_Name", data=working_no_2019, )
print(summary(fe_inst_1_country))

working_no_2019$predicted_log_GLP <- predict(fe_inst_1_country, new_data=working_no_2019$predicted_log_GLP)

fe_inst_2_country <- feols(Percent_of_female_borrowers ~ predicted_log_GLP | Country.x + Fiscal_Year, cluster="MFI_Name", data=working_no_2019)
print(summary(fe_inst_1_country))
```

```{r}
fe_inst_1_reg <- feols(log(Gross_Loan_Portfolio) ~ Cur_Interest_Rate | Region + Fiscal_Year, cluster="MFI_Name", data=working_no_2019, )
print(summary(fe_inst_1_reg))

working_no_2019$predicted_log_GLP <- predict(fe_inst_1_reg, new_data=working_no_2019$predicted_log_GLP)

fe_inst_2_reg <- feols(Percent_of_female_borrowers ~ predicted_log_GLP | Region + Fiscal_Year, cluster="MFI_Name", data=working_no_2019)
print(summary(fe_inst_2_reg))
```

```{r}
#Percent of female borrowers
theme_gtsummary_journal(journal = "qjecon")

mfi_fe_pct <- tbl_regression(time_mfi_fe_pct)
country_fe_pct <- tbl_regression(time_country_fe_pct)
region_fe_pct <- tbl_regression(time_region_fe_pct)

mfi_feiv_pct <- tbl_regression(fe_inst_2_mfi)
country_feiv_pct <- tbl_regression(fe_inst_2_country)
region_feiv_pct <- tbl_regression(fe_inst_2_reg)

theme_gtsummary_journal(journal = "qjecon")

pct_female_FE <- tbl_merge(
  tbls = list(mfi_fe_pct, country_fe_pct, region_fe_pct),
  tab_spanner = c("**MFI Fixed Effects**", "**Country Fixed Effects**", "**Region Fixed Effects**")
)

pct_female_FE_IV <- tbl_merge(
  tbls=list(mfi_feiv_pct, country_feiv_pct, region_feiv_pct),
  tab_spanner = c("**MFI Fixed Effects**", "**Country Fixed Effects**", "**Region Fixed Effects**")
)


pct_female_FEvsIV <- tbl_stack(
  tbls=list(pct_female_FE, pct_female_FE_IV),
  group_header = c("OLS", "IV")
  ) %>%
  as_gt() %>%
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups(groups = everything())
  ) %>%
  gt::tab_header(
    title=gt::md("**Regression Results for Percent of Female Borrowers**"),
    subtitle = gt::md("Data 2007-2018")
  ) %>%
  gt::fmt_number(
    columns=everything(),
    decimals = 4
  )
#

# print(rat_female_FEvsIV)
#
# print(pct_female_FE)
# print(pct_female_FE_IV)
print(pct_female_FEvsIV)
```

## Fraction of GLP to female borrowers
```{r}
#basic model, no fixed effects
basic_linear <- lm(Ratio_GLP_Female ~ Gross_Loan_Portfolio, data=working_no_2019)
print(summary(basic_linear))

basic_log <- lm(Ratio_GLP_Female ~ log(Gross_Loan_Portfolio), data=working_no_2019)
print(summary(basic_log))
```

Only Fixed Effects, no instrument
```{r}
#With time and mfi fixed effects
#the 0 means no instrumental variables
#what standard error clustering dim do i use (right now doing it by mfi)
time_mfi_fe_rat <- felm(Ratio_GLP_Female ~ log(Gross_Loan_Portfolio) | MFI_Name + Fiscal_Year | 0 | MFI_Name, working_no_2019)
print(summary(time_mfi_fe_rat))

time_country_fe_rat <- felm(Ratio_GLP_Female ~ log(Gross_Loan_Portfolio) | Country.x + Fiscal_Year | 0 | MFI_Name, working_no_2019)
print(summary(time_country_fe_rat))

#include region fixed effects
time_region_fe_rat <- felm(Ratio_GLP_Female ~ log(Gross_Loan_Portfolio) | Region + Fiscal_Year | 0 | MFI_Name, working_no_2019)
print(summary(time_region_fe_rat))
```

Fixed effects and instrument
Cross Sectional Fixed Effect by MFI
```{r}

fe_inst_1_rat_mfi <- feols(log(Gross_Loan_Portfolio) ~ Cur_Interest_Rate | MFI_Name + Fiscal_Year, cluster="MFI_Name", data=working_no_2019)
print(summary(fe_inst_1_rat_mfi))

working_no_2019$predicted_log_GLP <- predict(fe_inst_1_rat_mfi, new_data=working_no_2019$predicted_log_GLP)

fe_inst_2_rat_mfi <- feols(Ratio_GLP_Female ~ predicted_log_GLP | MFI_Name + Fiscal_Year, cluster="MFI_Name", data=working_no_2019)
print(summary(fe_inst_2_rat_mfi))
```

Cross Sectional Fixed Effect by Country
```{r}
fe_inst_1_rat_country <- feols(log(Gross_Loan_Portfolio) ~ Cur_Interest_Rate | Country.x + Fiscal_Year, cluster="MFI_Name", data=working_no_2019, )
print(summary(fe_inst_1_rat_country))

working_no_2019$predicted_log_GLP <- predict(fe_inst_1_rat_country, new_data=working_no_2019$predicted_log_GLP)

fe_inst_2_rat_country <- feols(Ratio_GLP_Female ~ predicted_log_GLP | Country.x + Fiscal_Year, cluster="MFI_Name", data=working_no_2019)
print(summary(fe_inst_2_rat_country))
```

Cross Sectional Fixed Effect by Region
This seems to be the only one that's nearly statistically significant- the others have very high p vals
```{r}
fe_inst_1_rat_reg <- feols(log(Gross_Loan_Portfolio) ~ Cur_Interest_Rate | Region + Fiscal_Year, cluster="MFI_Name", data=working_no_2019, )
print(summary(fe_inst_1_rat_reg))

working_no_2019$predicted_log_GLP <- predict(fe_inst_1_rat_reg, new_data=working_no_2019$predicted_log_GLP)

fe_inst_2_rat_reg <- feols(Ratio_GLP_Female ~ predicted_log_GLP | Region + Fiscal_Year, cluster="MFI_Name", data=working_no_2019)
print(summary(fe_inst_2_rat_reg))
```

```{r}
#ratio of female borrowers
#only fixed effects, no instrumented variable
theme_gtsummary_journal(journal = "qjecon")

mfi_fe_rat <- tbl_regression(time_mfi_fe_rat)
country_fe_rat <- tbl_regression(time_country_fe_rat)
region_fe_rat <- tbl_regression(time_region_fe_rat)

#with IV
mfi_feiv_rat <- tbl_regression(fe_inst_2_rat_mfi)
country_feiv_rat <- tbl_regression(fe_inst_2_rat_country)
region_feiv_rat <- tbl_regression(fe_inst_2_rat_reg)

rat_female_FE <- tbl_merge(
  tbls = list(mfi_fe_rat, country_fe_rat, region_fe_rat),
  tab_spanner = c("**MFI Fixed Effects**", "**Country Fixed Effects**", "**Region Fixed Effects**")
)

rat_female_FE_IV <- tbl_merge(
  tbls=list(mfi_feiv_rat, country_feiv_rat, region_feiv_rat),
  tab_spanner = c("**MFI Fixed Effects**", "**Country Fixed Effects**", "**Region Fixed Effects**")
)



rat_female_FEvsIV <- tbl_stack(
  tbls=list(rat_female_FE, rat_female_FE_IV),
  group_header = c("OLS", "IV")
  ) %>%
  as_gt() %>%
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups(groups = everything())
  )%>%
  gt::tab_header(
    title=gt::md("**Regression Results for Fraction of GLP to Female Borrowers**"),
    subtitle = gt::md("Data from 2007-2018")
  )


print(rat_female_FEvsIV)
```
IV coefficients
```{r}
#these are the coefficients on current interest rate in the instrumental variable regressions
#will show how good the instrument is

#Percent of female borrowers
cur_mfi_iv_pct <- tbl_regression(fe_inst_1_mfi)
cur_country_iv_pct <- tbl_regression(fe_inst_1_country)
cur_reg_iv_pct <- tbl_regression(fe_inst_1_reg)

pct_cur <- tbl_stack(
  tbls = list(cur_mfi_iv_pct, cur_country_iv_pct, cur_reg_iv_pct),
  group_header = c("MFI Fixed Effects", "Country Fixed Effects", "Region Fixed Effects")
) %>%
  bold_p() %>%
  as_gt() %>%
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups(groups = everything())
  )%>%
  gt::tab_header(
    title=gt::md("**Coefficients on Current Interest Rate**"),
    subtitle=gt::md("First Step of IV Regression of Percent of Female Borrowers, 2007-2018")
  ) %>%
  gt::fmt_number(
    columns=everything(),
    decimals = 4
  )

print(pct_cur)

#Ratio of GLP to female borrowers
cur_mfi_iv_rat <- tbl_regression(fe_inst_1_rat_mfi)
cur_country_iv_rat<- tbl_regression(fe_inst_1_rat_country)
cur_reg_iv_rat <- tbl_regression(fe_inst_1_rat_reg)

rat_cur <- tbl_stack(
  tbls = list(cur_mfi_iv_rat, cur_country_iv_rat, cur_reg_iv_rat),
  group_header = c("MFI Fixed Effects", "Country Fixed Effects", "Region Fixed Effects")
) %>%
  bold_p() %>%
  as_gt() %>%
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups(groups = everything())
  )%>%
  gt::tab_header(
    title=gt::md("**Coefficients on Current Interest Rate**"),
    subtitle=gt::md("First Step of IV Regression of Ratio of GLP to Female Borrowers, 2007-2018")
  ) %>%
  gt::fmt_number(
    columns=everything(),
    decimals = 4
  )

print(rat_cur)


```


```{r}
#to run all above
```

